Adapting the MVDR to a GPU for active sonar systems of different sizes.

### 2013-01-22 ASA2013/asa2013.tex
la2pdf commit - 2013:01:22	21:17:56	(Tue22.Jan)

In terms of computational complexity the diagonal loading factor is negligible, and will therefore be ignored from now on. Now let $x_l[n]$ represent the datavector from subarray $l$\todo{replace with with a drawing?},
\begin{gather}
\x_l[n] = \bmat{x_l[n] & x_{l+1}[n] & \dots & x_{l+L-1}[n]}\T,
\end{gather}
then a sample covariance matrix formed with temporal and spatial averaging, $\eR$, is given as:
\begin{gather}
\eR[n] =  \frac{1}{N_K N_L} \sumb{l=0}{M-L}\sumb{n'=n-K}{n+K} \x_l[n]\x_l\H[n] \in\mathbb{C}^{L,L},\label{spatialR}
\end{gather}
where $N_K = 2K+1$ is the number of temporal samples to perform averaging over, and $N_L = M-L+1$ is the number of subarrays. Finally, a fraction of the total power of $\eR[n]$ is added to its diagonal~\cite{Synnevag2007}.

Complexity: O($N_K N_L L^2$) and the inversion of O($L^3$)

>>>>

To arrive at a formulation of how $\eR$ is estimated, we first split the array into subarrays of length $L$ that overlap on all but one sensor. Let $x_l[n]$ represent the datavector from subarray $l$,
\begin{gather}
\x_l[n] = \bmat{x_l[n] & x_{l+1}[n] & \dots & x_{l+L-1}[n]}\T.
\end{gather}
Now the sample covariance matrix formed with temporal and spatial averaging, $\eR$, is given as:
\begin{gather}
\eR[n] =  \frac{1}{N_K N_L} \sumb{l=0}{N_L-1}\sumb{n'=n-K}{n+K} \x_l[n]\x_l\H[n] \in\mathbb{C}^{L,L},\label{spatialR}
\end{gather}
where $N_K = 2K+1$ is the number of temporal samples to perform averaging over, and $N_L = M-L+1$ is the number of subarrays. In the actual design a fraction of the total power of $\eR[n]$ is finally added to its diagonal~\cite{Synnevag2007}, but this step will be ignored here due to its negligible contribution to runtime.

\subsubsection{Complexity and implementation}

If (\ref{spatialR}) were to be implemented directly, then we note that the estimation step has a complexity of O($N_K N_L L^2$). By comparison the inversion is generally of O($L^3$), which implies that whenever $N_K\,N_L > L$ then the estimation step will dominate. Note that this inequality will increase as we increase the number of subarrays or temporal samples to perform averaging over.
